Intersection Type Algebras

### 2024-09-25 UTA/notes.tex

>>>>

\section{2024.09.12}

Questions we still need to figure out:
\begin{itemize}
  \item What to do about reflexive constraints?
  \item What if the list of types equal to the variable is empty?
  Should its solution be $\top$?
  \item If $e = e \to e$ is the "terminal" type algebra
  (any algebra can be mapped to it), admitting solution of any equation,
  does having a constraint like that in a given system mean we can simulate
  $\top = e$?
  \item If we have $e = e \to e$, and we also have a constraint $c = e \to c$,
  this is like saying $c = \top \to c$.  And $d = d \to e$ is "equivalent" to
   $d = d \to \top$?  Does this imply that every term can be typed as $d$ as well?
   (Probably the answer is no.)
   \item Supposing we substitute every variable that we can,
   being left with a system in which every type a variable is constrained to,
   contains that variable.  This might not yet be the proper SR, because we
   might still need to equate individual types in the list for each variable.
\end{itemize}
